\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-08-27 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updates

Our numerical simulations for the IEEE 14 bus system consider the following three cases:

\noindent\textbf{Case I.} Nominal case where ...

\noindent\textbf{Case II.} post-contingency simulation after the line 13 fails.

\noindent\textbf{Case III.}	load data are time-varying ...

>>>>

Our numerical simulations for the IEEE 14 bus system consider the following two cases:

\noindent\textbf{Case I.} {\red{Nominal case where ...}}

\noindent\textbf{Case II.} {\red{post-contingency simulation after the line 13 fails.}}

%\noindent\textbf{Case III.}	load data are time-varying ...
